\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items 
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands 

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Title} \rhead{Lead PI} \renewcommand{%
\headrulewidth}{0.0pt}



\centering {\bf Curriculum Vitae ({\emph{2-page limit}})}\\
{\bf ANN S. ALMGREN}\\
{\bf Mail Stop 50A-1148 \\
Lawrence Berkeley National Laboratory \\
Berkeley, CA 94720 \\
ASAlmgren@lbl.gov \\
510-486-5758} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt

PhD in Mechanical Engineering, University of California, Berkeley, 1991. \\
MS in Mechanical Engineering, University of California, Berkeley 1987.\\ 
BA in Physics, Harvard University, 1994.\\ 

}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt

1996--present Staff scientist with the Center for Computational Sciences and Engineering, Lawrence Berkeley National Laboratory \\ 
1992--1996 Staff researcher, Applied Mathematics Groups, Lawrence Livermore National Laboratory \\ 
1995--1996 Postdoctoral fellow, Applied Mathematics Groups, Lawrence Livermore National Laboratory \\ 
1991--1992 Visiting member of the School of Mathematics, Institute for Advanced Study \\

}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item C. M. Malone, M. Zingale, A. Nonaka, A. S. Almgren, and J. B. Bell, \newblock{ Multidimensional Modeling of Type I X-ray Bursts. II. Two-Dimensional Convection in a Mixed H/He Accretor},
\newblock{\em Astrophysical Journal}, 788, 115, 2014. \\ 
\item C. M. Malone, A. Nonaka, S. E. Woosley, A. S. Almgren, J. B. Bell, S. Dong, and M. Zingale, 
\newblock{ The Deflagration Stage of Chandrasekhar Mass Models for Type Ia Supernovae: I. Early Evolution},
\newblock{\em Astrophysical Journal}, \newblock{\bf 782}, 11, 2014.  \\ 
\item A. S. Almgren, J.B. Bell, M.J. Lijewski, Z. Lukic, E. Van Andel,
\newblock{ Nyx: A Massively Parallel AMR Code for Computational Cosmology},
\newblock {\em Astrophysical Journal}, 
{\bf 765}, 39, 2013. \\ 
\item M. Zingale, A. Nonaka, A. S. Almgren, J. B. Bell, C. Malone, and R. Orvedahl, 
\newblock{ Low Mach Number Modeling of Convection in Helium Shells on Sub-Chandrasekhar White Dwarfs. I. Methodology}, 
\newblock {\em Astrophysical Journal}, 
{\bf 764}, 97, 2013. \\ 
\item A. Nonaka, A. S. Almgren, J. B. Bell, M. J. Lijewski, C. M. Malone, and M. Zingale,
\newblock {\tt MAESTRO}: An Adaptive Low Mach Number Hydrodynamics Algorithm for
  stellar flows.
\newblock {\em Astrophysical Journal Supplement}, 
\newblock {\bf 188}, 358--383, 2010. \\ 
\end{enumerate} 

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt

My research focuses on the development and analysis of numerical methods for systems of partial 
differential equations arising in science and engineering.  I have made contributions in the
areas of finite volume methods, numerical discretizations of low Mach number flows, adaptive
mesh refinement and parallel computing.  A recent area of focus of my research has been on the
development of low Mach number models for stratified flows and their application to a number
of problems in astrophysics.  My work in this area spans a range of activities from deriving the
underlying partial differential equations to developing numerical algorithms for the resulting
systems to implementing high-performance parallel adaptive methodology.  
Several of the codes I have developed are used by researchers in the
astrophysics and cosmology communities.
}

%Synergistic Activities. A list of up to five examples that demonstrate
%the broader impact of the individual's professional and scholarly
%activities that focuses on the integration and transfer of knowledge
%as well as its creation.

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Member of two UC Santa Cruz Ph.D. thesis committees, 2009-2010.  \\ 
\item Chair of Luis W. Alvarez Postdoctoral Fellowship Selection Committee, 2010-11.  \\ 
\item AWM committee for selection of graduate student posters at 2006 Joint Meeting.  \\ 
\item SIAM representative to the Joint Committee on Women in the Mathematical Sciences.  \\ 
\item Reviewer/panelist for National Science Foundation, U.S. Department of Energy.  \\ 
\end{enumerate} 

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})} 
{\parindent 16pt

A. Adelmann (PSI)\\
A. Aspden (U. Portsmouth)\\
V. Beckner (LBNL)\\
J. Bell (LBNL)\\
H. Braun (U. G\"{o}ttingen)\\
A. Burrows (Princeton)\\
R. Camassa (UNC)\\
K. Chen (UCSC)\\
C. Gilet (U. Mich)\\
M. Duarte (LBNL)\\
M. Emmett (LBNL)\\
C. Joggerst (LANL)\\
M. Day (LBNL)\\
J. Dolence (Princeton)\\
S. Dong (UCSC)\\
D. Kasen (UCSC)\\
T. Kaman (PSI)\\
M. Lijewski (LBNL)\\
Z. Lukic (LBNL)\\
H. Ma (UCSC)\\
C. Malone (UCSC)\\
M. Minion (Stanford)\\
J. Niemeyer (U. G\"{o}ttingen)\\
A. Nonaka (LBNL)\\
J. Nordhaus (Rochester)\\
P. Nugent (LBNL/UCB)\\
D. Romps (LBNL/UCB)\\
W. Schmidt (U. G\"{o}ttingen)\\
R. Tiron (UCD)\\
S. Williams (LBNL)\\
S. Woosley (UCSC)\\
W. Zhang (LBNL)\\
M. Zingale (SUNYSB)

}


\end{flushleft}

\end{document}
