\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items 
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands 

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Approaching Exascale Models of Astrophysical Explosions
} \rhead{M.~Zingale} \renewcommand{%
\headrulewidth}{0.0pt}



\centering {\bf Curriculum Vitae}\\
{\bf JOHN B. BELL}\\
{\bf Lawrence Berkeley National Laboratory \\
Berkeley, CA 94720 \\
JBBell@lbl.gov \\
510-486-5391} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt

PhD in Mathematics, Cornell University, 1979. \\ 
MS in Mathematics, Cornell University, 1977. \\ 
BS in Mathematics, Massachusetts Institute of Technology, 1975. \\ 
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt

1996--present, Senior Staff Scientist and Group Lead for CCSE, LBNL \\ 
1993--1996, Director of the Center for Computational Sciences and Engineering, LLNL \\ 
1986--1993, Staff Ccientist, LLNL \\ 
1982--1986, Research Specialist, Exxon Production Research Co. \\
1979--1982, Research Mathematician, Naval Surface Weapons Center \\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item C. M. Malone, M. Zingale, A. Nonaka, A. S. Almgren, and J. B. Bell, "Multidimensional Modeling of Type I X-ray Bursts. II. Two-Dimensional Convection in a Mixed H/He Accretor", Astrophysical Journal, 788, 115, 2014. \\ 
\item C. M. Malone, A. Nonaka, S. E. Woosley, A. S. Almgren, J. B. Bell, S. Dong, and M. Zingale, "The Deflagration Stage of Chandrasekhar Mass Models for Type Ia Supernovae: I. Early Evolution", Astrophysical Journal, 782, 11, 2014. \\ 
\item M. Zingale, A. Nonaka, A. S. Almgren, J. B. Bell, C. Malone, and R. Orvedahl, ``Low Mach Number Modeling of Convection in Helium Shells on Sub-Chandrasekhar White Dwarfs. I. Methodology", Astrophysical Journal, 764, 97, 2013. \\
\item C. Gilet, A.S. Almgren, J.B. Bell, A. Nonaka, S.E. Woosley and M. Zingale, "Low-Mach Number Modeling of Core Convection in Massive Stars", Astrophysical Journal, 773, 137, 2013. \\ 
\item Haitao Ma, Stan Woosley, Chris Malone, Ann Almgren, and J.B. Bell, "Carbon Deflagration in Type Ia Supernovae: I. Centrally Ignited Models", Astrophysical Journal, 771, 58, 2013. \\ 
\end{enumerate} 

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt

My research focuses on the development and analysis of
numerical methods for partial differential equations arising in science and engineering.
I have made contributions in the areas of finite difference methods, numerical methods for low Mach number flows, adaptive mesh refinement, interface tracking and parallel computing.
I have also worked on the application of these numerical methods to problems
from a broad range of fields, including combustion, shock physics, seismology, flow in porous media and astrophysics. 
Recently, my work has focused on the development of new computational approaches for coupling different physical processes and the design of algorithms that combine models at different scales in a single computation.  

}

%Synergistic Activities. A list of up to five examples that demonstrate
%the broader impact of the individual's professional and scholarly
%activities that focuses on the integration and transfer of knowledge
%as well as its creation.

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Chair, AMS von Neumann Symposium, July 2011. \\
\item Member, NAS Combustion Infrastructure Study, December 2008 -- December 2011.\\
\item Chair, SIAM Computational Science and Engineering Activity Group, Jan.1, 2007 - Dec. 31, 2008.\\
\item Managing editor, Comm. in Applied Math. and Comput. Science, June 1, 2005 - present.\\
\item Co-Chair, SIAM Annual Meeting, July 2004. \\ 
\end{enumerate} 

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})} 
{\parindent 16pt

A. Almgren (LBNL) \\ A. Aspden (Cranfield U.) \\ V. Beckner (LBNL) \\ P.-T. Bermer (LLNL) \\
A. Burrows (Princeton) \\ C. Chan (LBNL) \\ J. Chen (SNL) \\ 
R. Cheng (LBNL) \\ C. Joggerst (LANL) \\ 
M. Day (LBNL) \\ A. Donev (CIMS) \\ S. Dong (UCSC) \\ M. Duarte (LBNL) \\ 
A. Garcia (SJSU) \\  J. Goodman (NYU) \\ R. Grout (NREL) \\
D. Kasen (UCSC) \\ C. Law (Princeton) \\ M. Lijewski (LBNL) \\
Z. Lukic (LBNL) \\
H. Ma (UCSC) \\ C. Malone (LANL) \\ M. Minion (Stanford) \\ J. Niemeyer (U. G\"{o}ttingen) \\ 
A. Nonaka (LBNL) \\ P. Nugent (LBNL) \\ G. Pau (LBNL) \\ V. Pascucci (Utah) \\ K. Pruess (LBNL) \\
D. Quinlan (LLNL) \\
V. Sankaran (SNL) \\ W. Schmidt (U. G\"{o}ttingen) \\
J. Shalf (LBNL) \\
S. Tachibana (JAXA) \\ D. Unat (LBNL) \\ E. Vanden-Eijnden (CIMS) \\
S. Williams (UNC) \\ S. Williams (LBNL) \\ S. Woosley (UCSC) \\ W. Zhang (LBNL) \\ 
M. Zingale (SUNYSB)

%Collaborator name, current institution \\
%Collaborator name, current institution \\
}
\

\end{flushleft}

\end{document}
