\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
%\usepackage{blindtext} % To create text
%\usepackage{mdwlist} % mdwlist for compact enumeration/list items 
%\usepackage[pagestyles]{titlesec} % related with sections—namely titles, headers and contents
\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\large}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}

\usepackage{caption}
\captionsetup{labelsep=period}

\pagestyle{fancy} % allows you to use the header and footer commands 

\raggedright
\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.

\pagestyle{fancy} \lhead{Curriculum Vitae, Daniel Kasen} \rhead{Co-I} \renewcommand{%
\headrulewidth}{0.0pt}



\centering 
{\bf Daniel Kasen}\\
{\bf Department of Physics  \\
  366 LeConte Hall MS 7300 \\
  University of California, Berkeley \\
  Berkeley, CA, 94720-7300
} \smallskip

\begin{flushleft} {\bf Professional Preparation}
{\parindent 16pt

PhD: University of California, Berkeley, Physics,  2004.\\ 
MS: University of California, Berkeley, Physics,  2001.\\ 
BS: Stanford University, 1997. \\
}

\vspace{.04in}
{\bf Appointments}
{\parindent 16pt

2010--present, Assistant Professor, Department of Physics, University of California, Berkeley \\
2010--present, Assistant Professor, Department of Astronomy, UC, Berkeley \\
2010--present, Faculty Scientist, Nuclear Science Division, LBNL \\
2007--2010, Hubble postdoctoral fellow, University of California, Santa Cruz \\
2004--2007, Allan C. Davis postdoctoral fellow, Johns Hopkins University and Space Telescope Science Institute, Baltimore, MD \\
}

\vspace{.04in}
{\bf Five Publications Most Relevant to This Proposal}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt

\item ''Type Ia Supernovae from Merging White Dwarfs. II. Post-merger Detonations'', Raskin, C., Kasen, D., 
Moll, R., Schwab, J., Woosley, S.E., \emph{Astrophys. J.}, {\bf 788}, 75 (2014).

\item "Type Ia Supernovae from Merging White Dwarfs. I. Prompt Detonations", 
Moll, R., Raskin, C., Kasen, D.,  Woosley, S.E., \emph{Astrophys. J.}, {\bf 785}, 105 (2014).

\item "A Compact Degenerate Primary-star Progenitor of SN 2011fe", Bloom, J., Kasen, D., et al., \emph{Astrophys. J.}, {\bf 744}, 17 (2012).

\item  ``The Diversity of Type~Ia Supernovae from Broken Symmetries'', Kasen, D., Ropke, F., and Woosley, S.E., \emph {Nature},  {\bf 460}, 869 (2009).

\item `Time Dependent Monte Carlo Radiative Transfer Calculations For
3-Dimensional Supernova Spectra, Lightcurves, and Polarization'', Kasen, D., Thomas, R.C., \& Nugent, P., \emph{Astrophys. J.}, {\bf 651}, 366 (2006). 

\end{enumerate} 

\vspace{-6pt}
{\bf Research Interests and Expertise}
{\parindent 16pt
Computational and theoretical nuclear astrophysics; Modeling of thermonuclear supernovae, neutron star mergers, and other explosive astrophysical transients; Multi-dimensional radiation transport using implicit monte carlo techniques;  Analysis of supernova spectra and light curves as a means to validate hydrodynamical simulations and infer nucleosynthetic yields. 
}

%Synergistic Activities. A list of up to five examples that demonstrate
%the broader impact of the individual's professional and scholarly
%activities that focuses on the integration and transfer of knowledge
%as well as its creation.

\vspace{.04in}
{\bf Synergistic Activities}
\vspace{-6pt}
\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
\item Co-director, UC High-Performance AstroComputing summer school on Computational Explosive Astrophysics, (6/2012).
\item Co-organizer, "Fast and Furious" Workshop on Supernovae and Peculiar Transients, Aspen Center for Physics, (6/2014).
\item Department of Energy Presidential Early Career Award recipient (2013).
\item Member of NERSC executive users group (2011-present).
\item Referee for Nature, the Astrophysical Journal, the Astronomical Journal, Astronomy and Astrophysics, NMRAS (ongoing).
\end{enumerate} 

\vspace{-6pt}
{\bf Collaborators ({\emph{past 5 years including name and current institution}})} 
{\parindent 16pt
Carlos Badenes (Princeton),
John Bell (LBNL),
Lars Bildsten (UCSB),
Sergei Blinnikov (MPA Garching),
Stephane Blondin (France),
Josh Bloom (Berkeley),
Jason Dexter (UCB)
Alexei Filippenko (UCB),
Ryan Foley (Illinois),
Michele Fumagalli (Carnegie),
Peter Garnavich (Notre Dame),
Avishai Gal-Yam (Jerusalem), 
Gary Glatzmaier (UCSC),
James Guillochon (UCSC),
Brian Hayden (Notre Dame),
Alex Heger (U. Minnesota)
Wolfgang Hillebrandt (MPA Garching),
Tabetha Hole (East Tenessee State),
Phil Hopkins (Caltech),
Andy Howell (LCOGT),
Richard Kessler (Chicago),
Io Kleiser (Caltech),
Greg Laughlin (UCSC),
Avi Loeb (Harvard),
Keichi Maeda (IPMU),
Brian Metzger (Princeton),
Rainer Moll (MPA),
Ken Nomoto (University of Tokyo),
Ken Nordsieck (University of Wisconsin),
Peter Nugent (LBNL),
Tony Pan (Harvard),
Eliot Quataert (UCB),
Enrico Ramirez-Ruiz (UCSC),
Cody Raskin (LBNL),
Armin Rest (STScI),
Fritz Ropke (MPA Garching),
Stephan Rosswog (Bremman) ,
Nathan Roth (UCB),
Evan Scannapieco (ASU),
Ken Shen (UCB),
Rollin Thomas (LBNL),
}


\end{flushleft}

\end{document}
