\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.
\usepackage{hyperref}  %The ability to create hyperlinks within the document

\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}   % Essential for adding images to you document.

\usepackage[numbers]{natbib}

%\usepackage{sectsty}
%% \sectionfont{\normalsize}
%% \subsectionfont{\normalsize}
%\subsubsectionfont{\normalsize \it}

\usepackage[small,compact]{titlesec}
\titlespacing{\subsubsection}{0pt}{0.5em}{0.25em}
\titlespacing{\subsection}{0pt}{0.5em}{0.5em}
\titlespacing{\section}{0pt}{0.5em}{0.5em}
\titlespacing{\paragraph}{0pt}{0.75em}{0.25em}

\titleformat*{\subsubsection}{\itshape}


\let\oldthebibliography=\thebibliography
  \let\endoldthebibliography=\endthebibliography
  \renewenvironment{thebibliography}[1]{%
    \begin{oldthebibliography}{#1}%
      \setlength{\parskip}{0.25ex}% 
      \setlength{\itemsep}{0.25ex}% 
  }%
  {% 
    \end{oldthebibliography}% 
  }



\usepackage{caption}
\captionsetup{labelsep=period}

\setlength{\parskip}{0.125\baselineskip}%
%\setlength{\parindent}{0pt}%

\input newcommands

%\raggedright


\begin{document}


%\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.


\pagestyle{fancy} 
\lhead{Approaching Exascale Models of Astrophysical Explosions} 
\rhead{PI: Zingale} \renewcommand{%
\headrulewidth}{0.0pt}

\begin{center}
\bf {PERSONNEL JUSTIFICATION AND MANAGEMENT PLAN} 
\end{center}


\section{PERSONNEL JUSTIFICATION}

%% What personnel are already in place and what are their roles on the
%% project? If applicable, describe personnel that will be hired on the
%% project in the future and their responsibilities. The INCITE program
%% welcomes proposals from individual PIs or teams of collaborators.

All personnel are in place.  Our team spans 4 institutions (Stony
Brook, Los Alamos National Laboratory, Lawrence Berkeley National
Laboratory, and UC Santa Cruz).  We have been collaborating together
for more than 10 years on problems related to those proposed here.
Furthermore, we (together will additional collaborators at these same
institutions) represent the principal authors of the two simulation
codes used here, \maestro\ and \castro.


\begin{tightitem}
\item {\bf Michael Zingale} will act as the lead for this project.  He
  will collaborate on all of the science applications, work on
  development and maintenance of the two simulation codes as needed
  for this project, and run simulations of the XRB.

\item {\bf Ann Almgren} will work on code development of both \maestro\
  and \castro\ in support of the proposed problems.  She will also be
  involved in the scientific analysis of the simulations proposed here.

\item {\bf John Bell} will be the main contact with the \boxlib\ group
  at LBNL.  We will work with John to incorporate performance
  improvements into \maestro\ and \castro.  John will also directly be
  involved in the scientific analysis of the simulations proposed
  here.

\item {\bf Alan Calder} will work primarily on the analysis and
  simulation design of the \castro\ white dwarf merger and
  black widow pulsar simulations.
  Alan will also be a lead on the ``extra'' exploratory applications
  proposed here, particularly the URCA calculations.

\item {\bf Brian Freisen}

\item {\bf Adam Jacobs} is a SBU graduate student doing his thesis on
  the sub-Chandra SNe Ia convection.  Adam will be the lead scientist
  on this problem.  Adam is also the lead developer of the GPU version
  of the reaction networks.

\item {\bf Dan Kasen} will perform post-processing radiation transfer
  calculations on the explosion results with \sedona, generating
  lightcurves and spectra.

\item {\bf Max Katz} is a SBU graduate student doing his thesis on the
  white dwarf merger problem with \castro.  Max will be the lead
  scientist on this problem.  Max is also the lead developer of 
  the GPU version of the equation of state.

\item {\bf Chris Malone} will be the lead scientist on the XRB problem
  with \maestro\ (Chris did his PhD thesis on \maestro\ XRB simulations
  in 2D).  Chris will also assist in the reaction network development.

\item {\bf Bronson Messer}

\item {\bf Thomas Papatheodore}

\item {\bf Stan Woosley} will collaborate on all of the science
  applications here and provide initial models and microphysics needed
  for the proposed simulations and assist in the analysis.

\item {\bf Weiqun Zhang}

\end{tightitem} 

\section{MANAGEMENT PLAN}

We have been working together for over 10 years (you'll find many of
the names here on the list of publications under the current INCITE
award).  Although we identified leads for each of the science problems
above, we will all be involved in the science analysis and we expect
many of the CoIs here to be co-authors on the publications that result
from the proposed simulations.
Allocation of computing resources will primarily follow the breakdown 
of time estimated in the narrative.  As we work closely together and are
in frequent contact, we do not expect any tensions or issues with the 
distribution of this time.

For the code development, the SBU group travels to LBNL several times
a year to plan the development path of \maestro\ and \castro, and we 
make frequent contact with each other through e-mail and phone conferencing.
All of the codes are managed by the git version control system and we
use regular regression testing to ensure that the code continues to
perform as expected while undergoing development.
PI Zingale will be the primary contact dealing with the management of
the award and preparing reports.  We expect that the graduate students
here will take a lead role in presenting the results to the community
at conferences, and to be the lead authors in the publications that result.

%% Describe the project's leadership team and how decisions are made to
%% allocate time to individuals or, for proposals with multiple
%% collaborating teams, subgroups within the project. Describe the focus
%% of each individual or subgroup. Successful proposals will include a
%% management plan that conveys to reviewers the interrelationship
%% between subgroups and how the sum of the parts will lead to scientific
%% discovery or engineering solutions that are the overarching goal of
%% the project. Also identify points of contact who will provide updates
%% on the status of the work including publications, awards, and
%% highlights of accomplishments.



\end{document}
