\documentclass[11pt,letterpaper,english]{article}
\usepackage[T1]{fontenc} % Standard package for selecting font encodings
\usepackage{txfonts} % makes spacing between characters space correctly
\usepackage{xcolor} % Driver-independent color extensions for LaTeX and pdfLaTeX.

\usepackage{fancyhdr} % header footer placement

\usepackage[top=1in, bottom=1in, left=1in, right=1in] {geometry} % Margins
\usepackage{graphicx}  % Essential for adding images to you document.

\usepackage{sectsty}
\sectionfont{\normalsize}
\subsectionfont{\normalsize}
\subsubsectionfont{\normalsize \it}


\setlength{\parskip}{\baselineskip}%
\setlength{\parindent}{0pt}%

\pagestyle{fancy} % allows you to use the header and footer commands


\begin{document}

\setlength{\parindent}{0in} % Amount of indentation at the first line of a paragraph.


\pagestyle{fancy} 
\lhead{Approaching Exascale Models of Astrophysical Explosions} 
\rhead{PI: Zingale} \renewcommand{%
\headrulewidth}{0.0pt}

\begin{center}
{\bf PUBLICATIONS RESULTING FROM INCITE AWARDS} \\
(last three years only)
\end{center}

\begin{itemize}

                                                                               
\item {\em Low Mach Number Modeling of Convection in Helium Shells on
  Sub-Chandrasekhar White Dwarfs II: Bulk Properties of Simple Models,
} A.~M.~Jacobs, M.~Zingale, A.~Nonaka, A.~S.~Almgren, \& J.~B.~Bell
  2016, accepted to ApJ

\item {\em Double White Dwarf Mergers on Adaptive Meshes
  I. Methodology and Code Verification, } M.~P.~Katz, M.~Zingale,
  A.~C.~Calder, F.~D.~Swesty, A.~S.~Almgren, W.~Zhang 2016, ApJ, 819,
  94.

\item {\em Comparisons of Two- and Three-Dimensional Convection in
  Type I X-ray Bursts} M.~Zingale, C.~M.~Malone, A.~Nonaka,
  A.~S.~Almgren, \& J.~B.~Bell 2015, ApJ, 807, 60.

\item {\em Multidimensional Modeling of Type I X-ray
  Bursts. II. Two-Dimensional Convection in a Mixed H/He Accretor, }
  C.~M.~Malone, M.~Zingale, A.~Nonaka, A.~S.~Almgren, \& J.~B.~Bell
  2014, ApJ, 788, 115.

\item {\em Type Ia Supernovae from Merging White
  Dwarfs. II. Post-merger Detonations}, Raskin, C., Kasen, D., Moll,
  R., Schwab, J., \& Woosley, S.~E., 2014, ApJ, 788, 75

\item {\em Type Ia Supernovae from Merging White Dwarfs. I. Prompt Detonations},
  Moll, R., Raskin, C., Kasen, D., \& Woosley, S.~E., 2014, ApJ, 785, 105

\item {\em The Deflagration Stage of Chandrasekhar Mass Models for
  Type Ia Supernovae. I. Early Evolution}, Malone, C. M., Nonaka, A.,
  Woosley, S.~E., Almgren, A.~S., Bell, J.~B., Dong, S., \& Zingale, M.,
  2014, ApJ, 782, 11


\end{itemize}

\end{document}
